A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2020-10-12 03_smoothing_tracks.Rmd

# # make basic plot with rectangle
# fig_bounds <-
#   ggplot()+
#   geom_point(data = data_errors,
#             aes(x, y),
#             size = 0.1, alpha = 0.2, 
#             col = "grey")+
#   geom_path(data = data,
#             aes(x, y),
#             size = 0.1)+
#   geom_hline(yintercept = c(0.6, 0.8),
#              col = "grey20",
#              lty = 2, lwd = 0.2)+
#   coord_equal(expand = F) +
#   ggthemes::theme_map()

# # append to first figure
# figure_median_smooth[[1]] <-
#   figure_median_smooth[[1]]+
#   annotation_custom(grob = ggplotGrob(fig_bounds),
#                     ymin = 0.6, ymax = 0.8,
#                     xmin = 0.5, xmax = 0.7)

# wrap plots
# fig_median_smooth <- 
  # wrap_plots(figure_median_smooth, 
  #            ncol = 3)+
  # plot_annotation(tag_levels = "a",
  #                 tag_prefix = "(",
  #                 tag_suffix = ")") &
  # theme(plot.tag = element_text(face = "bold"))

@@

  return(data_return)
})
```

@@

# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_jitter(aes(factor(interval), speed),
              col = pal[1],
              shape = 4, alpha = 0.5)+
  geom_boxplot(aes(factor(interval), speed),
               fill = NA,
               show.legend = F, 
               width = 0.3, 
               outlier.size = 0.2)+
  geom_hline(yintercept =
               c(mean(data$speed, na.rm = T),
                 quantile(data$speed, na.rm = T,
                          probs = c(0.95))
               ),
             lty = c(1, 2))+
  scale_y_log10(label = scales::comma)+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```

>>>>

@@

  return(data_return)
})

# get mean speed estimate and sd
speed_agg_smooth <- 
  lapply(list_of_agg, function(df) {
    na.omit(df)
    df[, speed := atl_get_speed(df)]
    df[, list(median = median(speed, na.rm = T),
              sd = sd(speed, na.rm = T),
              interval = first(interval))]
  })

# bind
speed_agg_smooth <- rbindlist(speed_agg_smooth)
```

@@

# show boxplot of speed
fig_agg_speed <-
  ggplot(data_agg)+
  geom_jitter(aes(factor(interval), 1 + speed),
              col = pal[1],
              shape = 4, alpha = 0.5)+

  geom_hline(yintercept =
               1 + quantile(data$speed, na.rm = T,
                        probs = c(0.5, 0.95)),
             lty = c(1, 2))+
  geom_errorbar(data = speed_agg_smooth,
                aes(x = factor(interval),
                    ymin = 1 + median - sd,
                    ymax = 1 + median + sd),
                width = 0.2,
                position = position_nudge(x = 0.25)) +
  geom_point(data = speed_agg_smooth,
             aes(x = factor(interval),
                 y = 1 + median),
             shape = 21,
             size = 3,
             fill = pal[3],
             position = position_nudge(x = 0.25)) +
  geom_boxplot(aes(factor(interval), 1 + speed),
               position = position_nudge(x = -0.25,),
               fill = pal[2],
               alpha = 0.5,
               show.legend = F, 
               width = 0.25, 
               outlier.size = 0.2)+
  scale_y_log10(label = scales::comma,
                limits = c(NA, 1.005))+
  ggthemes::theme_few()+
  theme(axis.text.y = element_blank())+
  labs(x = "interval (s)",
       y = "speed")
```
